\documentclass[12pt]{article}
\renewcommand{\familydefault}{\sfdefault}

\usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\usepackage{hyperref}


\begin{document}
% ---------- First Page (flush right) ----------
\thispagestyle{empty} % no header/footer on first page
\begin{flushright}
\Huge SNAPSHOT OBJECTIVES \\
\vspace{2cm}
BOE Sidewalk Assessment \\
\vspace{6cm}
Prepared For \\
\vspace{0.5cm}
\normalsize City of Los Angeles, Bureau of Engineering \\
\vspace{2cm}
\large Prepared By \\
\vspace{0.5cm}
\normalsize Joe Miranda - David Hernandez - Jose Carpinteyro - Douglas Sanchez \\
\vspace{2cm}
\large 7 December 2025
\end{flushright}

\newpage % move to next page
\tableofcontents
\newpage

% First snapshot
\section{\Large Snapshot 1 — Start Objective}

\textbf{}{Purpose:}
Define the foundation and establish everything needed for the first 4 months of project work.

\subsection{Goals for Snapshot 1:}
\begin{itemize}
    \item Select and finalize the project topic.
    \item Establish the main objective of the project.
    \item Determine project timeline (6 or 12 months).
    \item Assign responsibilities to each team member.
    \item Identify the core framework, base dependencies, and tools needed.
    \item Build the initial workflow diagram showing how the system operates at a high level.
    \item Set up Jira, create tasks for the first sprint, and log potential bugs for later TestRail coverage.
    \item Begin writing initial versions of the SDD, SRS, User Manual (README), and Design Spec.
\end{itemize}

\subsection{Deliverables for Snapshot 1:}
\begin{itemize}
    \item Initial SDD
    \item Initial SRS
    \item README (User Manual) – first draft
    \item Design Spec – first draft
    \item Snapshot 1 Objective Document (this section)
    \item First workflow diagram
    \item Initial Jira sprint and backlog
    \item List of base dependencies
    \item Identified areas for future testing/bugs
\end{itemize}

% Second Snapshot
\newpage

\section{\Large Snapshot 2 - Develop First Feature}
\textbf{Purpose:}
Expand the project by adding the first major new feature and update all documentation to reflect progress.

\subsection{Goals for Snapshot 2:}
\begin{itemize}
    \item Add one additional large feature or objective to the project.
    \item Create new development tasks related to the added feature.
    \item Add new dependencies, packages, or libraries needed for the new functionality.
    \item Update the workflow diagram to reflect new system behavior.
    \item Update all documentation (SDD, SRS, User Manual, Design Spec) with details from the new feature.
    \item Begin TestRail documentation for this checkpoint.
\end{itemize}

\subsection{Deliverables for Snapshot 2:}
\begin{itemize}
    \item Updated SDD
    \item Updated SRS
    \item Updated User Manual
    \item Updated Design Spec
    \item Updated Workflow Diagram
    \item Snapshot 2 Objective Document
    \item TestRail: Snapshot 2 test run + summary report
\end{itemize}

% Third Snapshot
\newpage

\section{\Large Snapshot 3 - System Improvements}
\textbf{Purpose:}
Iteratively improve the system by expanding on the first major feature and start testing components.

\subsection{Goals for Snapshot 3:}
\begin{itemize}
    \item Refine first feature components and integrations
    \item Add new dependencies and required libraries.
    \item Update the workflow diagram to reflect all cumulative features.
    \item Continue updating the SDD, SRS, User Manual, and Design Spec.
    \item Add TestRail test cases and produce the required run report.
\end{itemize}

\subsection{Deliverables for Snapshot 3:}
\begin{itemize}
    \item Updated SDD
    \item Updated SRS
    \item Updated User Manual
    \item Updated Design Spec
    \item Updated Workflow Diagram
    \item Snapshot 3 Objective Document
    \item TestRail: Snapshot 3 test run + summary report
\end{itemize}

% Final Snapshot
\newpage

\section{\Large Snapshot 4 - Finalize testing and documentation}
\textbf{Purpose:}
Complete all final integration steps, finalize documentation, and record future work.

\subsection{Goals for Snapshot 4:}
\begin{itemize}
    \item Finish any outstanding tasks or remaining feature adjustments.
    \item Add the last project objective update and finalize all documentation.
    \item Include a “Future Work” section describing improvements not finished before the deadline.
    \item Ensure that all dependencies, libraries, and modules are fully documented.
    \item Finalize the user manual and design spec for final submission.
    \item Complete the final TestRail test run and summary.
    \item Ensure the workflow diagram accurately reflects the complete system.
\end{itemize}

\subsection{Deliverables for Snapshot 4:}
\begin{itemize}
    \item Updated SDD (final)
    \item Updated SRS (final)
    \item Updated User Manual (final)
    \item Updated Design Spec (final)
    \item Updated Workflow Diagram (final)
    \item Snapshot 4 Objective + Reflection Document
    \item TestRail: Snapshot 4 test run + summary report
    \item “Future Work” section
\end{itemize}

\end{document}